---
title: "spectrum.data"
author: "daniellembecker"
date: "12/13/2018"
output: rmarkdown::github_document
---


#Making graphs to show the spectrum gradient for blue light, multi light and both blue and multi light in terms of wavelenth and intensity

#clear list
```{r}
rm(list=ls())
```

#set wd

```{r}
setwd ("~/Desktop/Repositories/Light_Spectrum")
```

#load libraries
```{r}
library(dplyr)
library(tidyr)
library(ggplot2)
```

#load data

```{r}
mydata <- read.csv("~/Desktop/Repositories/Light_Spectrum/Data/bluelight.spectra.csv")
#View(mydata)
```

#line graph of data for blue light spectrum
```{r}
ggplot(data=mydata, aes(x=wavelength, y=intensity)) + geom_line(aes(group=1)) + scale_y_continuous(expand=c(0,0), limits=c(0, 4000)) + scale_x_continuous(limits=c(350, 1000)) 
```
#For future use:
# Change color of both line and points
# Change line type and point type, and use thicker line and larger points
# Change points to circles with white fill
#ggplot(data=dat, aes(x=time, y=total_bill, group=1)) + geom_line(colour="red", linetype="dashed", size=1.5) + geom_point(colour="red", size=4, shape=21, fill="white")

#load data

```{r}
mydata <- read.csv("~/Desktop/Repositories/Light_Spectrum/Data/multilight.spectra.csv")
#View(mydata)
```

#line graph of data for multi light spectrum
```{r}
ggplot(data=mydata, aes(x=wavelength, y=intensity)) + geom_line(aes(group=1))+ scale_y_continuous(expand=c(0,0), limits=c(0, 2500)) + scale_x_continuous(limits=c(350, 1000)) 
```

#load data

```{r}
mydata <- read.csv("~/Desktop/Repositories/Light_Spectrum/Data/blueandmulti.spectra.csv")
#View(mydata)
```

#line graph of data for both blue and multi light spectrum
```{r}
ggplot(data=mydata, aes(x=wavelength, y=intensity)) + geom_line(aes(group=1)) + scale_y_continuous(expand=c(0,0), limits=c(0, 4000)) + scale_x_continuous(breaks = seq(350,1000,50))
```